\documentclass[alan.tex]{subfiles}
\begin{document}
  \item \textbf{BMW CarIT GmbH}, Ulm, Germany (October 2012 - Present)\\
    \emph{C++, C, Python}
    \begin{my_desc}
      \item[Core Architecture Team] for the next BMW Head-Unit. (December 2014 - Present)
        \begin{my_bullets}
          \item Responsibilities in the team include requirement elicitation, architecture design,
            technology reviews/decisions, coordination of multiple domains to evaluate and drive technical
            decisions and various technical tasks needed on different phases. Some notable examples are:
            \begin{my_bullets}
            \item Responsible for the centralization of the systemd unit files and the system configuration,
              developing and maintaining the Yocto recipes to control the deployment on the different head
              unit images, wrote tests to verify running configuration against specified configuration and
              reviewing any changes done.
            \item Drove the collection of requirements for the application framework, setting up of the team
              and designing/reviewing the framework architecture.
            \end{my_bullets}
        \end{my_bullets}
      \item[Security Engineer] (June 2014 - January 2015)
        \begin{my_bullets}
          \item Requirement review.
          \item Evaluated technologies to use (for example SELinux vs AppArmor) and worked on the security architecture
            for the Head Unit.
          \item Participated in the evaluation of several suppliers and in the clarification of requirements with
            them during the supplier offer phase.
        \end{my_bullets}
      \item[Developer] for Head-Unit connectivity components; bluetooth device management and telephony manager (May 2013 - May 2014)
        \begin{my_bullets}
          \item Worked in a team re-factoring the two Linux daemons from C to C++.
          \item While developing for these components I was heavily involved in training colleagues on git/gerrit
              workflow and C++11 features.
        \end{my_bullets}
      \item[Developer] for Bluetooth (October 2012 - May 2013)
        \begin{my_bullets}
        \item Bluetooth / BlueZ (C).  Worked on a proof of concept for AVRCP 1.5 for BlueZ (ver. 5).
            In parallel provided bug fixes upstream and supported GENIVI discussions to define the
            GENIVI Bluetooth API.
          \item Bluetooth testing framework (python). Designed and implemented a testing framework to
            test BMW specific use cases. The framework was designed to be able to support different backends and
            Bluetooth profiles.
        \end{my_bullets}
      \item[Member] of the BMW CarIT core interview team. I was part of a team with the responsibility to review phone interviews
        conducted by other colleagues, schedule and organize on-site interviews and train more developers to do interviews.
      \item[Mentoring] of a student during their internship. The student became an active part of the developing
        team implementing and testing different features. After completing their internship they continued with their bachelor thesis
        under my supervision.
    \end{my_desc}
\end{document}
